---
title: "experiments_notes_cuts"
author: "Katherine Piatti"
date: "4/6/2021"
output: html_document
---


## xts

i found several resources advising doing time series anaylsis using xts objects. i tried that first, but am finding it too hard to figure out. i am cutting and pasting the stuff i did with that and adding it here in case i was to use it later.



### Create Tsibble

```{r}
span2007_2009TS <- as_tsibble(span2007_2009, index = date_time)

span2007_2009TS
```


*Missing Values*

```{r}
#check for missing values
span2007_2009TS %>% 
  has_gaps()

# count gaps/blanks (i.e.implicit missing values)
span2007_2009TS %>% 
  count_gaps()


#fill gaps with 0
span2007_2009TS <- span2007_2009TS %>% 
  fill_gaps(.full = TRUE)

span2007_2009TS %>% 
  has_gaps()
```




======================================================
EXPERIMENTATION
===============================================

## can i filter out every 10 minutes from a date-time object

lubridate functions that select elements of date-time objects
hour( )
year()
month()
week()
yearmonth()
min

```{r}
# fail
yrs2007_2009 %>% 
  filter(yrs2007_2009$date_time %in% minute(c(1, 10, 20)))
```


```{r}
#fail 
yrs2007_2009 %>% 
  filter(minutes(yrs2007_2009$date_time == 10))
```

```{r}
minute(yrs2007_2009$date_time)
# extracts vector of minute values in date_time
```



```{r}
minutes <- minute(yrs2007_2009$date_time)

yrs2007_2009 %>% 
  filter(minutes %in% c(0, 10, 20, 30, 40, 50))
```
```{r}

```




```{r}
hms_yrs07_09 <- yrs2007_2009 %>% 
  separate("time", c("hours", "min", 'sec'), sep = ":") 




glimpse(hms_yrs07_09)
```

```{r}
hist(hms_yrs07_09$min)
```


```{r}
yrs2007_2009 %>% 
  filter(min == c(0:60))
```


```{r}
days <- day(yrs2007_2009$date_time)

unique(days)
```

```{r}
seconds <- second(yrs2007_2009$date_time)

unique(seconds)
```

```{r}
fml <- minute(TSyrs_long$date_time)

TSyrs_long %>% 
  filter(fml == C(1, 10, 20, 30, 40, 50, 59))

```





